---
title: "API Methods"
author: "Lukas Burk"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{API Methods}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
editor_options:
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
	collapse = TRUE,
	comment = "#>",
	echo = FALSE
)

library(tRakt)
library(kableExtra)
library(purrr)
library(dplyr)
library(stringr)
```

```{r api-list}
api <- system.file("api-methods.yml", package = "tRakt") |>
	yaml::read_yaml()

api <- api |>
	map(\(section) {
		section |>
			map(tibble::as_tibble) |>
			list_rbind(names_to = "Method")
	}) |>
	list_rbind(names_to = "Section")


n_implemented <- sum(api$implementation != "none" & !str_starts(api$implementation, "\\?"))
n_total <- nrow(api)

format_api_table <- function(xdf) {
	xdf |>
		mutate(
			endpoint = glue::glue("<a href = '{url}'>{endpoint}</a>"),
			Method = str_to_title(Method),
			Method = str_replace_all(Method, "^Id\\s", "ID "),
			implementation = if_else(
				implementation == "none",
				"",
				glue::glue("<code>{implementation}</code>")
			),
			authentication = if_else(
				!is.na(authentication),
				cell_spec("Required", bold = TRUE, color = "white", background = "red"),
				cell_spec("Optional", bold = FALSE, color = "white", background = "green")
			),
		) |>
		select(
			-url,
			Endpoint = endpoint,
			Auth = authentication,
			Implementation = implementation
		)
}

print_api_table <- function(xdf) {
	xdf |>
		kbl(escape = FALSE) |>
		kable_styling(
			position = "center",
			bootstrap_options = c("striped", "hover"),
			full_width = TRUE
		)
}
```

This is a reference list of [trakt.tv API methods](https://trakt.docs.apiary.io/) tracked by this package, their endpoint URLs (with user-specified parameters indicated by a `:` prefix) and their implementation status.
Methods with an implementation link are available in this package; blank entries are tracked but not yet implemented.
Authenticated methods are indicated as such.

Write-only endpoints (creating/updating/deleting items, scrobbling, check-ins) are omitted as they are outside the scope of this package.

Currently **`r n_implemented`** of **`r n_total`** tracked GET endpoints are implemented.

# Search

```{r api-search}
api |>
	filter(Section == "search") |>
	select(-Section) |>
	format_api_table() |>
	print_api_table()
```

# Movies

```{r api-movies}
api |>
	filter(Section == "movies") |>
	select(-Section) |>
	format_api_table() |>
	print_api_table()
```

# Shows

```{r api-shows}
api |>
	filter(Section == "shows") |>
	select(-Section) |>
	format_api_table() |>
	print_api_table()
```

## Seasons

```{r api-shows-seasons}
api |>
	filter(Section == "seasons") |>
	select(-Section) |>
	format_api_table() |>
	print_api_table()
```

## Episodes

```{r api-shows-episodes}
api |>
	filter(Section == "episodes") |>
	select(-Section) |>
	format_api_table() |>
	print_api_table()
```

# People

```{r api-people}
api |>
	filter(Section == "people") |>
	select(-Section) |>
	format_api_table() |>
	print_api_table()
```

# Users

```{r api-users}
api |>
	filter(Section == "users") |>
	select(-Section) |>
	format_api_table() |>
	print_api_table()
```

# Comments

```{r api-comments}
api |>
	filter(Section == "comments") |>
	select(-Section) |>
	format_api_table() |>
	print_api_table()
```

# Lists

```{r api-lists}
api |>
	filter(Section == "lists") |>
	select(-Section) |>
	format_api_table() |>
	print_api_table()
```

# Recommendations

```{r api-recommendations}
api |>
	filter(Section == "recommendations") |>
	select(-Section) |>
	format_api_table() |>
	print_api_table()
```

# Misc

These endpoints are used to check filter arguments. The output is cached in tidied up
format as package datasets.

```{r api-misc}
api |>
	filter(
		Section %in%
			c(
				"certifications",
				"countries",
				"genres",
				"languages",
				"networks"
			)
	) |>
	format_api_table() |>
	select(-Auth) |>
	print_api_table()
```
