---
title: "Show Analysis: 24"
author: "Lukas Burk"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE, warning = FALSE, error = FALSE,
  out.width = "100%"
)
```

```{r startup}
library(tRakt)
library(tibble) # For glimpse()
```

## Step 1: Search

Use the search function to find the show you're looking for.

```{r 24_search}
show_info <- trakt.search("24", "show")
show_info
```

## Step 2: Use the ID

Use the `trakt` ID (recommended over other IDs) for subsequent API calls.  
In this case, we'll use `trakt.seasons.summary()` to get data for all seasons of the show, while also getting an additional list-column containing all episode data, which includes user ratings.

```{r 24_getting_seasons}
seasons <- trakt.seasons.summary(target = show_info$trakt, extended = "full", episodes = TRUE)
glimpse(seasons)
```

## Step 3: Tidying up

We're interested in the `episodes` list-column, which needs unnesting. In this case we can simply use `dplyr::bind_rows` to take the list of `tbls` that is `seasons$episodes` and basically `rbind` them all together, meaning the result is a `tibble` of the episode data we care about.

```{r 24_episodes_unnesting}
library(dplyr) 

episodes <- bind_rows(seasons$episodes)
glimpse(episodes)
```

## Step 4: Graph!

Now we have our episode data in a tidy form, might as well look at it.

```{r 24_episodes_plot}
library(ggplot2)

ggplot(data = episodes, aes(x = episode, y = rating, color = votes)) +
  geom_point(size = 3) +
  facet_wrap(~season, nrow = 1, labeller = label_both, scales = "free_x") +
  scale_x_continuous(breaks = scales::pretty_breaks()) +
  scale_y_continuous(breaks = seq(0, 10, .5), minor_breaks = seq(0, 10, .25), limits = c(7, 9)) +
  scale_color_viridis_c() +
  labs(title = "24: Episode Ratings on trakt.tv",
       subtitle = "Episode ratings by trakt.tv users by season",
       x = "Episode Number", y = "Rating (0-10)", color = "# of Votes",
       caption = "jemus42.github.io/tRakt") +
  theme_minimal() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(size = rel(.6)))
```

