---
title: "Show Analysis: 24"
author: "Lukas Burk"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteEncoding{UTF-8}
  %\VignetteIndexEntry{Show Analysis: 24}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
	collapse = TRUE,
	comment = "#>",
	message = FALSE,
	warning = FALSE,
	error = FALSE,
	out.width = "100%"
)
```

```{r startup}
library(tRakt)
library(dplyr)
library(ggplot2)
```

## Step 1: Search

Use the search function to find the show you're looking for. 
The show "24" is a particularly good example for a show with a bad name, because If we just search for "24", we'll get a wrong result due to ambiguity.  
To nudge the search function to find the show we're looking for, we can specify the year of release:

```{r 24-search}
show_info <- search_query("24", years = 2001, type = "show")
show_info
```

Now we have the basic show info to work with, including the `title` and various IDs.


## Step 2: Use the ID

Use the `trakt` ID for subsequent API calls, which is guaranteed to be always available and unique on trakt.tv.  
Now we'll use `seasons_summary()` to get data for all seasons of the show, while also getting an additional list-column containing all episode data, which includes user ratings.

```{r 24-getting-seasons}
seasons <- seasons_summary(show_info$trakt, extended = "full", episodes = TRUE)
glimpse(seasons)
```

## Step 3: Tidying up

We're interested in the `$episodes` list-column, which needs unnesting. In this case we can use `dplyr::bind_rows()` to take the list of `tibble`s and `rbind` them all together, meaning the result is a `tibble` of the episode data we care about.

```{r 24-episodes-unnesting}
episodes <- bind_rows(seasons$episodes)
glimpse(episodes)
```

## Step 4: Graph!

Now we have our episode data in a tidy form, might as well look at it.

```{r 24-episodes-plot}
ggplot(data = episodes, aes(x = episode, y = rating, color = votes)) +
	geom_point(size = 3, alpha = 2 / 3) +
	facet_wrap(~season, nrow = 1, scales = "free_x") +
	scale_x_continuous(breaks = c(1, 10, 20), expand = c(0, 3)) +
	scale_y_continuous(breaks = seq(0, 10, .5), minor_breaks = seq(0, 10, .25), limits = c(7, 9)) +
	scale_color_viridis_c() +
	guides(color = guide_colorbar(barwidth = unit(6, "cm"), title.vjust = .75)) +
	labs(
		title = "24: Episode Ratings on trakt.tv",
		subtitle = "Episode ratings by trakt.tv users by season",
		x = "Episode Number",
		y = "Rating (1-10)",
		color = "# of Votes",
		caption = "jemus42.github.io/tRakt"
	) +
	theme_minimal() +
	theme(
		plot.title.position = "plot",
		legend.position = "bottom"
	)
```
