---
title: "Getting Started"
author: "Lukas Burk"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE, warning = FALSE, error = FALSE,
  out.width = "100%"
)
```

## First step: Loading packages and trakt.tv credentials

```{r startup}
library(tRakt)
library(tibble) # For glimpse()
```


## Case Study: "24"

Step 1: Use the search function to find the show you're looking for.

```{r 24_search}
show_info <- trakt.search("24", "show")
show_info
```

Step 2: Use the `trakt` ID (recommended over other IDs) for subsequent API calls.  
In this case, we'll use `trakt.seasons.summary()` to get data for all seasons of the show, while also getting an additional list-column containing all episode data, which includes user ratings.

```{r 24_getting_seasons}
seasons <- trakt.seasons.summary(target = show_info$trakt, extended = "full", episodes = TRUE)
glimpse(seasons)
```

Step 3: Unpacking `episodes`.  
We're interested in the `episodes` list-column, which needs unnesting. In `tidyr::unnest()`, we use `.sep = "_"`, which will prepend `episodes_` to all the variables names in the nested list-column. This is recommended because the variables names will clash with the variables names already present in the `seasons` dataset.

```{r 24_episodes_unnesting}
library(tidyr) # for unnest()

episodes <- unnest(seasons, episodes, .sep = "_")
glimpse(episodes)
```

Step 4: We can graph our results!

```{r 24_episodes_plot}
library(ggplot2)

ggplot(data = episodes, aes(x = episodes_episode, y = episodes_rating, color = episodes_votes)) +
  geom_point(size = 3) +
  facet_wrap(~season, nrow = 1, labeller = label_both) +
  scale_x_continuous(breaks = seq(4, 24, 4)) +
  scale_y_continuous(breaks = seq(0, 10, .5), minor_breaks = seq(0, 10, .25), limits = c(7, 9)) +
  scale_color_viridis_c() +
  labs(title = "24: Episode Ratings on trakt.tv",
       subtitle = "Episode ratings by trakt.tv users by season",
       x = "Episode Number", y = "Rating (0-10)", color = "# of Votes") +
  theme_minimal() +
  theme(legend.position = "bottom")
```

