---
title: "The Basics"
author: "Lukas Burk"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE, warning = FALSE, error = FALSE,
  out.width = "100%"
)
```

## Preamble: The trakt.tv API and this package


## Getting data from trakt.tv

### 1. Loading packages and trakt.tv credentials

```{r startup}
library(tRakt)
```

That's all you need to to for basic things. If you're planning a larger project with lots and lots of data retrieval, you might want to create your own API app [on trakt.tv](https://trakt.tv/oauth/applications) and use `trakt_credentials` to set your `client id`.

### 2. Find things

#### Via direct search

```{r search}
# Text search
trakt.search("Game of Thrones", type = "show")
# Search by explicit ID
trakt.search.byid("121361", id_type = "tvdb", type = "show")
```

#### Via whatever's popular(ish)

Another scenario would be that you're not necessarily interested in some specific media item, but rather a collection of items that fulfill certain criteria, like being popular on trakt.tv and maybe being from a specific period or genre and whatnot. While you can also filter `trakt.search` by other criteria, it's maybe more useful to filter, let's say, the most watched movies of the past week by the release year of the movie.

```{r auto-lists}
# The 5 most popular shows
trakt.popular(type = "shows", limit = 5)
# The 10 most watched (during the past week) movies from 1990-2000
trakt.watched(type = "movies", period = "weekly", years = c(1990, 2000))
```

